Twists of supersymmetric gauge theories

### 2020-01-08 paper.tex
Some 4d edits

\subsection{$\mc N = 1$ Super Yang-Mills Theory with Matter}
We begin by treating $\mc N=1$ Super Yang-Mills theory with gauge group $G$, with a matter (half) hypermultiplet valued in a symplectic representation $U$.  This is the theory obtained from 6d $\mc N=(1,0)$ super Yang-Mills theory with matter, after dimensional reduction to 5 dimensions.

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=1$ super Yang-Mills by restricting the 6d fields from section \ref{6d_10_section} to representations of the group $\mr O(5)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^5; \gg)$, and a scalar $\phi' \in \Omega^1(\RR^5; \gg)$.
 \item $U$-valued bosons: a (symplectic) scalar field $\phi \in \Omega^0(\RR^5; W \otimes U)$.
 \item $\gg$-valued fermions: a spinor $\lambda \in \Omega^0(\RR^5; S \otimes W \otimes \gg)$.
 \item $U$-valued fermions: a spinor $\psi \in \Omega^0(\RR^5; S \otimes W \otimes U)$.
\end{itemize}

@@

\paragraph{Fields:} We can describe the BRST fields of $\mc N=2$ super Yang-Mills by restricting the fields of maximal super Yang-Mills from 10d, or alternatively by restricting the 7d $\mc N=1$ fields from section \ref{7d_section}, to representations of the group $\mr O(5)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item Bosons: A gauge field $A \in \Omega^1(\RR^5; \gg)$, and five scalars $\phi_1 ,\ldots, \phi_5 \in \Omega^1(\RR^5; \gg)$.
 \item Fermions: A pair of spinors $\lambda_1$ and $\lambda_2$ in $\Omega^0(\RR^5; S \otimes W \otimes \gg)$.
\end{itemize}
We could alternatively have obtained these fields by considering the $\mc N=1$ 5d super Yang-Mills theory, with matter valued in the symplectic representation $T^*\gg$.

@@

\subsection{$\cN=2$ Super Yang-Mills with hypermultiplet matter}
%quaternionic is hyperkahler
%pseudo-real is quaternionic

>>>>

\subsection{$\mc N = 1$ Super Yang-Mills Theory with Matter}  \label{5d_1_section}
We begin by treating $\mc N=1$ Super Yang-Mills theory with gauge group $G$, with a matter (half) hypermultiplet valued in a symplectic representation $U$.  This is the theory obtained from 6d $\mc N=(1,0)$ super Yang-Mills theory with matter, after dimensional reduction to 5 dimensions.

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=1$ super Yang-Mills by restricting the 6d fields from section \ref{6d_10_section} to representations of the group $\mr O(5)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^5; \gg)$, and a scalar $\phi' \in \Omega^1(\RR^5; \gg)$.
 \item $U$-valued bosons: a (symplectic) scalar field $\phi \in \Omega^0(\RR^5; W \otimes U)$.
 \item $\gg$-valued fermions: a spinor $\lambda \in \Omega^0(\RR^5; S \otimes W \otimes \gg)$.
 \item $U$-valued fermions: a spinor $\psi \in \Omega^0(\RR^5; S \otimes U)$.
\end{itemize}

@@

\paragraph{Fields:} We can describe the BRST fields of $\mc N=2$ super Yang-Mills by restricting the fields of maximal super Yang-Mills from 10d, or alternatively by restricting the 7d $\mc N=1$ fields from Section \ref{7d_section}, to representations of the group $\mr O(5)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item Bosons: A gauge field $A \in \Omega^1(\RR^5; \gg)$, and five scalars $\phi_1 ,\ldots, \phi_5 \in \Omega^1(\RR^5; \gg)$.
 \item Fermions: A pair of spinors $\lambda_1$ and $\lambda_2$ in $\Omega^0(\RR^5; S \otimes W \otimes \gg)$.
\end{itemize}
We could alternatively have obtained these fields by considering the $\mc N=1$ 5d super Yang-Mills theory, with matter valued in the symplectic representation $T^*\gg$.

@@

\subsection{$\cN=2$ Super Yang-Mills with Matter}

We obtain $\mc N=2$ super Yang-Mills theory on $\RR^4$ by dimensionally reducing $\mc N=(1,0)$ super Yang-Mills from $\RR^6$, or $\mc N=1$ super Yang-Mills from $\RR^5$, with a hypermultiplet valued in a symplectic representation $U$.  In these terms we can describe the BRST fields.

\vspace{-10pt}
\paragraph{Fields:}  We can describe the BRST fields of $\mc N=2$ super Yang-Mills with matter valued in the symplectic representation $U$ by restricting the 5d $\mc N=2$ fields from Section \ref{5d_1_section} to representations of the group $\mr O(4)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(\phi_1,\phi_2) \in \Omega^1(\RR^4; \gg)^2$.
 \item $U$-valued bosons: a $W$-valued scalar field $\phi \in \Omega^0(\RR^4; W \otimes U)$.
 \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
 \item $U$-valued fermions: a Dirac spinor $\psi \in \Omega^0(\RR^4; (S_+\oplus S_-) \otimes U)$.
\end{itemize}
